---
title: "heat_network_statistics_emissions"
author: "Jakub Kowalczyk"
date: "2023-05-17"
output: html_document
---

```{r setup, include=FALSE}
# Options ==== 

knitr::opts_chunk$set(echo = F, 
                      error = F, 
                      warning = F)

options(digits=2) # two decimal points 
options(scipen=999) # disable scientific notation, specifically important for unique property reference numbers (UPRNs)

# Packages ==== 

libraries <- c("tidyverse", "janitor", "kableExtra", "patchwork", "sgplot")
lapply(libraries, require, character.only = T)



# Data Load ====

hnmbr_full <- read_csv("C:/Users/u453623/Documents/OFFLINE/heat_network_statistics/data/HNMBR_2018-2022_CLEANED.csv")

ghg_conv_factors <- read_csv("C:/Users/u453623/Documents/OFFLINE/heat_network_statistics/data/ghg_conv_factors.csv")

# Theme for plots

sgplot::use_sgplot()
```

To calculate an estimate of how much heat networks contribute to emission reductions we will: 

1) Estimate current emissions on a network level based on generation, fuel type & emissions factors from GSG 

2) Estimate the emissions for each domestic connection as if they were all on gas boilers instead of networks .

## 1) Estimate Heat Network Emissions 

```{r}

#selecting the variables that are needed 

hnmbr_emissions_variables <- hnmbr_full %>% 
  select(propert_name_heat_network, uprn, primary_energy_source, primary_tech_type, generation_heating_hot_water, customers_residential, total_customers, heat_network_customers)

```

```{r}
#TODO: Issue with formatting of primary_energy_source variable

hnmbr_emissions_variables <- hnmbr_emissions_variables %>% 
  mutate(primary_energy_source = gsub("[^[:alnum:]]", "", tolower(primary_energy_source)))

hnmbr_emissions_variables <- hnmbr_emissions_variables %>% 
  mutate(primary_energy_source)


```


```{r}

#calculating current emissions contribution 

# generation * emissions_factor[based on fuel type per network]? 

network_emissions_table <- hnmbr_emissions_variables %>% 
  group_by(primary_energy_source) %>% 
  summarise(number_of_networks = n(), 
            generation_per_network_fuel = sum(generation_heating_hot_water, na.rm = T))

```

We do not expect: 
- ambient heat 
- waste heat 

to have a contribution to emissions 

For oil, GHG conversion factor of LPG was used (closest to Kerosene I could think of (or google)). 

For networks with "other" fuel types, I was not able to discern what fuel they use, therefore we cannot estimate contribition to emissions. 

```{r}

network_emissions_table <- network_emissions_table %>% 
  inner_join(ghg_conv_factors, by = c("primary_energy_source" = "Fuel_type")) 

network_emissions_table <- network_emissions_table %>% 
  mutate(kg_CO2e = generation_per_network_fuel * GHG_emissions_factor)

# lets remove the 0s

network_emissions_table <- network_emissions_table %>% 
  filter(kg_CO2e > 0)

```

Does TDCV account for boiler efficiency.


