---
title: "heat_network_statistics_emissions"
author: "Jakub Kowalczyk"
date: "2023-05-17"
output: html_document
---

```{r setup, include=FALSE}
# Options ==== 

knitr::opts_chunk$set(echo = F, 
                      error = F, 
                      warning = F)

options(digits=2) # two decimal points 
options(scipen=999) # disable scientific notation, specifically important for unique property reference numbers (UPRNs)

# Packages ==== 

libraries <- c("tidyverse", "janitor", "kableExtra", "patchwork", "sgplot")
lapply(libraries, require, character.only = T)



# Data Load ====

hnmbr_full <- read_csv("C:/Users/u453623/Documents/OFFLINE/heat_network_statistics/data/HNMBR_2018-2022_CLEANED.csv")

ghg_conv_factors <- read_csv("C:/Users/u453623/Documents/OFFLINE/heat_network_statistics/data/ghg_conv_factors.csv")

# Theme for plots

sgplot::use_sgplot()
```

To calculate an estimate of how much heat networks contribute to emission reductions we will: 

1) Estimate current emissions on a network level based on generation, fuel type & emissions factors from GSG 

2) Estimate the emissions for each domestic connection as if they were all on gas boilers instead of networks .

## 1) Estimate Heat Network Emissions 

```{r}

#selecting the variables that are needed 

hnmbr_emissions_variables <- hnmbr_full %>% 
  select(propert_name_heat_network, uprn, primary_energy_source, primary_tech_type, generation_heating_hot_water, customers_residential, total_customers, heat_network_customers)

# code below fixes issue with formatting of primary_energy_source variable

hnmbr_emissions_variables <- hnmbr_emissions_variables %>% 
  mutate(primary_energy_source = gsub("[^[:alnum:]]", "", tolower(primary_energy_source)))




```


```{r}

#calculating current emissions contribution 

# generation * emissions_factor[based on fuel type per network]? 

network_emissions_table <- hnmbr_emissions_variables %>% 
  group_by(primary_energy_source) %>% 
  summarise(number_of_networks = n(), 
            generation_per_network_fuel = sum(generation_heating_hot_water, na.rm = T))

```

We do not expect: 

- ambient heat 
- waste heat 

to have a contribution to emissions. They were removed from the rest of this table to avoid unnecessary information cluttering. 

*For oil, GHG conversion factor of LPG was used (closest to Kerosene I could think of (or Google)). 

For networks with "other" fuel types, I was not able to discern what fuel they use, therefore we cannot estimate contribution to emissions. These networks were removed. 

```{r}
network_emissions_table <- network_emissions_table %>% 
  inner_join(ghg_conv_factors, by = c("primary_energy_source" = "Fuel_type")) 

network_emissions_table <- network_emissions_table %>% 
  mutate(kg_CO2e = generation_per_network_fuel * GHG_emissions_factor)

# lets remove the 0s

network_emissions_table <- network_emissions_table %>% 
  filter(kg_CO2e > 0)

network_emissions_table
```

This table represents the total emissions contributions for all networks we could calculate. 


```{r}

total_CO2e_kg_all_networks <- pluck(sum(network_emissions_table$kg_CO2e))


total_CO2e_kg_all_networks

```

The total emission contribution of heat networks is equal to `r total_CO2e_kg_all_networks` / one hundred seventeen million nine hundred seven thousand three hundred ten kilograms of CO2e

## 2) Estimating emissions reduction associated with being on a network. 

In order to estimate how much emission reduction is associated with being on a heating network, we have to estimate the associated emissions contribution of not being on a network i.e. each connected customer being on an individual gas boiler. 

Because of large variance within non-domestic building stock, we cannot confidently estimate emissions on a customer-connection level. 

As an alternative, we will estimate the emissions reductions associated with being on a network within domestic connections.

### Procedure

To do this, we will use values from domestic connections 

Based on the number of domestic connections, we will calculate the amount of emissions those connections would contribute using a range of typical daily consumption values (TDCVs) and the green-house gas conversion factors for natural gas. This will give us a range of estimates of how much we could expect domestic connections to contribute to emissions IF they were on individual gas boilers. 

Next, we will calculate the actual supply received for all of these domestic networks, and calculate the emissions contribution. 

Then, we will calculate the % difference in the associated emissions between the alternative scenario and the current data

This % difference will then be applied to the remaining, non-domestic connections. 

We will then combine both estimates for domestic and non-domestic contributions to emissions based on individual gas boilers, and compare this against the actual emissions contributions figure above. 

```{r}
# First, we create a subset of the hnmbr emissions variables only containing domestic connections 

hnmbr_emissions_variables_domestic <- hnmbr_emissions_variables %>% 
  filter(customers_residential > 0)

hnmbr_emissions_variables_domestic

```

The most recent TDCV update (2020) sets TDCV for gas at 8000, 12000, 17000 at low, medium and high respectively.

https://www.ofgem.gov.uk/publications/decision-typical-domestic-consumption-values-2020

```{r}

#creating a table to store TDCV values

TDCV <- data_frame(
  category = c("low", "medium", "high"), 
  value = c(8000, 12000, 17000)
)

```

```{r}

# calculating total amount of domestic connections 

domestic_connection <- pluck(sum(hnmbr_emissions_variables$customers_residential))

```

```{r}

# now we will build up our estimate of domestic contributions towards emissions 

domestic_network_emissions_table <- TDCV %>% 
  rowwise() %>% 
  mutate(total_domestic_connections = domestic_connection,
         total_supply_kwh = value * domestic_connection) 

domestic_network_emissions_table
```

Here, total supply is calculated as the TDCV value multiplied by the number of total dommestic connections. 

```{r}

gas_ghg_conv_factor <- pluck(ghg_conv_factors, 2,5)

domestic_network_emissions_table <- domestic_network_emissions_table %>% 
  mutate(natural_gas_conversion = gas_ghg_conv_factor, 
         kg_CO2e = total_supply_kwh * natural_gas_conversion)

domestic_network_emissions_table

```

From this, we receive three values of emissions contributions based on low, medium and high TDCVs. 

We can now calculate the % change between heat network associated emissions compared to each domestic connection having a gas boiler. 

```{r}

domestic_network_emissions_table <- hnmbr_emissions_variables_domestic %>% 
  group_by(primary_energy_source) %>% 
  summarise(number_of_networks = n(), 
            generation_per_network_fuel = sum(generation_heating_hot_water, na.rm = T)) %>% 
  inner_join(ghg_conv_factors, by = c("primary_energy_source" = "Fuel_type")) %>% 
  mutate(kg_CO2e = generation_per_network_fuel * GHG_emissions_factor) %>% 
  filter(kg_CO2e > 0)

domestic_network_emissions_table

total_CO2e_kg_domestic_networks <- pluck(sum(domestic_network_emissions_table$kg_CO2e))

```
```{r}
#TODO: After lunch break - have a look at the missing values in generation and consider how much that is affecting the networks. Although more generation values would be driving this even higher. 
```

