---
title: 'Heat Networks '
date: "`r Sys.Date()`"
sgtemplates:
  datatables:
    features:
      info: yes
      ordering: yes
      paging: yes
      searching: no
  header:
    phase_banner:
      tag: WIP
      text: This is a work in progress.
    site_branding: Scottish Government
  metadata:
    label: Report
  navigation:
    toc:
      sticky: no
output:
  word_document:
    toc: yes
    toc_depth: '2'
  html_document:
    code_download: no
    df_print: paged
    fig_caption: yes
    number_sections: no
    self_contained: no
    template: _template.html
    toc: yes
    toc_depth: 2
    toc_float: no
---

```{r setup, include = FALSE}

# Options ==== 

knitr::opts_chunk$set(echo = F, 
                      error = F, 
                      warning = F)

options(digits=2) # two decimal points 
options(scipen=999) # disable scientific notation, specifically important for unique property reference numbers (UPRNs)

# Packages ==== 

libraries <- c("tidyverse", "janitor", "kableExtra", "patchwork", "sgplot")
lapply(libraries, require, character.only = T)



# Data Load ====

#TODO: locate and load all data

# Theme for plots

sgplot::use_sgplot()
```

- The Heat Networks Act (2021) sets  out a target for 2.6 TWh of heat to be supplied via heat networks by 2027 and 6TWh by 2030. 

- The Heat Networks Metering and Billing Regulations (here on now referred to as HNMBR) provide the main source of data on heat supply via heat networks. 

- Since taking effect in 2014, there have been 2 cycles of HNMBR, one spanning from 2014-2018 (referred to as the 2018 data cycle), and one spanning 2018-2022 (referred to as the 2022 data cycle)

- The most recent cycle has recently been concluded, giving an opportunity to analyse progress towards targets set out by the Heat Networks Act (2021)

- TODO: ALSO SOME INTEREST IN CONTRIBUTION TO EMISSIONS REDUCTIONS. 

In the below note, an outline is provided on the updates the latest batch of data provides. 

## Contribution to Emissions Reductions 








## Network and Customer Number Statistics

### Number of Networks

- The 2018 data cycle contained XXXX heat networks 
- The 2022 data cycle contained XXXX heat networks
- This is a XX% drop networks reported

### Number of Network Types

Below is a graph representing the number of networks grouped by network type (domestic, non-domestic and mixed).

```{r}



```

### Number of Customers and Buildings 

Below is a graph representing the number of customers and total buildings

```{r}

```

### Number of Customers (by type)


