---
title: 'Heat Networks '
date: "`r Sys.Date()`"
sgtemplates:
  datatables:
    features:
      info: yes
      ordering: yes
      paging: yes
      searching: no
  header:
    phase_banner:
      tag: WIP
      text: This is a work in progress.
    site_branding: Scottish Government
  metadata:
    label: Report
  navigation:
    toc:
      sticky: no
output:
  word_document:
    toc: yes
    toc_depth: '2'
  html_document:
    code_download: no
    df_print: paged
    fig_caption: yes
    number_sections: no
    self_contained: no
    template: _template.html
    toc: yes
    toc_depth: 2
    toc_float: no
---

```{r setup, include = FALSE}

# Options ==== 

knitr::opts_chunk$set(echo = F, 
                      error = F, 
                      warning = F)

options(digits=2) # two decimal points 
options(scipen=999) # disable scientific notation, specifically important for unique property reference numbers (UPRNs)

# Packages ==== 

libraries <- c("tidyverse", "janitor", "kableExtra", "patchwork", "sgplot")
lapply(libraries, require, character.only = T)



# Data Load ====

hnmbr_2018 <- read_csv("C:/Users/u453623/Documents/OFFLINE/heat_network_statistics/data/HNMBR_2015-2018.csv")

hnmbr_2022 <- read_csv("C:/Users/u453623/Documents/OFFLINE/heat_network_statistics/data/HNMBR_2018-2022_CLEANED.csv")

#LCHD 

hnmbr_matched <- read_csv("C:/Users/u453623/Documents/OFFLINE/heat_network_statistics/data/HNMBR_2018-2022_MATCHED_446.csv")

# Theme for plots

sgplot::use_sgplot()
```

- The Heat Networks Act (2021) sets  out a target for 2.6 TWh of heat to be supplied via heat networks by 2027 and 6TWh by 2030. 

- The Heat Networks Metering and Billing Regulations (here on now referred to as HNMBR) provide the main source of data on heat supply via heat networks. 

- Since taking effect in 2014, there have been 2 cycles of HNMBR, one spanning from 2014-2018 (referred to as the 2018 data cycle), and one spanning 2018-2022 (referred to as the 2022 data cycle)

- The most recent cycle has recently been concluded, giving an opportunity to analyse progress towards targets set out by the Heat Networks Act (2021)

In the below note, an outline is provided on the updates the latest batch of data provides. 

## QA Note 

QA figures: % missing for capacity, generation, supply, buildings customers, technology and fuel. 

## Total Buildings and and customer numbers

```{r}

hnmbr_2022 %>% 
  summarise(total_buildings = sum(total_buildings, na.rm = T), 
            total_customers = sum(total_customers, na.rm = T))
  
```

### By network type

```{r}

# ==== Formatting ====

customer_number_variables <- c("customers_residential", "customers_industrial", "customers_commercial", "customers_public", "customers_other") 
building_number_variables <- c("buildings_residential", "buildings_industrial", "buildings_commercial", "buildings_public", "buildings_other")

hnmbr_2022 <- hnmbr_2022 %>% 
  mutate(customers_non_domestic = customers_industrial + customers_commercial + customers_public + customers_other, 
         buildings_non_domestic = buildings_industrial + buildings_commercial + buildings_public + buildings_other)

hnmbr_2022 <- hnmbr_2022 %>%  
  mutate(heat_network_type = case_when(
    customers_residential != 0 & customers_non_domestic == 0 ~ as.character("Domestic"),
    customers_non_domestic != 0 & customers_residential == 0 ~ as.character("Non-domestic"), 
    customers_residential != 0 & customers_non_domestic != 0 ~ as.character("Mixed"),
    TRUE ~ as.character("Unknown")))

# ==== number of networks table ====

number_of_networks_by_network_type <- hnmbr_2022 %>% 
  group_by(heat_network_type) %>% 
  summarise(number_of_networks = n())

```

## Total Capacity, Generation and Supply 

```{r}
hnmbr_2022 %>% 
  summarise(total_capacity_units = sum(capacity_heating_hot_water, na.rm = T), 
            total_generation_kwh = sum(generation_heating_hot_water, na.rm = T), 
            total_supply_kwh = sum(supply_heating_hot_water, na.rm = T))
```
### Number of Missing values 

```{r}
hnmbr_2022 %>% 
  summarise(capacity = sum(is.na(capacity_heating_hot_water)),
            generation = sum(is.na(generation_heating_hot_water)), 
            supply = sum(is.na(supply_heating_hot_water)))
```

### Imputed Capacity, Generation and Supply

```{r}
hnmbr_2022 %>% 
  summarise(supply_missing = sum(is.na(imputed_supply_perc)), 
            supply_present = sum(!is.na(imputed_supply_perc)))
```


### By network type 

```{r}
hnmbr_2022 %>% 
  group_by(heat_network_type) %>% 
  summarise(total_capacity_units = sum(capacity_heating_hot_water, na.rm = T), 
            total_generation_kwh = sum(generation_heating_hot_water, na.rm = T), 
            total_supply_kwh = sum(supply_heating_hot_water, na.rm = T)) 
```

### By technology 

```{r}

# formatting ====

hnmbr_2022 <- hnmbr_2022 %>% 
  mutate(primary_tech_type_cleaned =gsub("[^[:alnum:]]", "", tolower(primary_tech_type))) %>% 
  mutate(primary_tech_type_cleaned = case_when(primary_tech_type == "CHP engine" ~ "CHP", 
                                               primary_tech_type == "CHP Steam Turbine or Steam Screw Expander" ~ "CHP", 
                                               primary_tech_type == "Engine-driven CHP" ~ "CHP",
                                               primary_tech_type_cleaned == "heatexchangerfromwasteheatrecoveryprocess" ~ "wasteheat",
                                               TRUE ~  primary_tech_type_cleaned))


# table ===== 

hnmbr_2022 %>% 
  group_by(primary_tech_type_cleaned) %>% 
  summarise(total_capacity_units = sum(capacity_heating_hot_water, na.rm = T), 
            total_generation_kwh = sum(generation_heating_hot_water, na.rm = T), 
            total_supply_kwh = sum(supply_heating_hot_water, na.rm = T)) 
```
### By fuel 

```{r}

# formatting ==== 

hnmbr_2022 <- hnmbr_2022 %>% 
  mutate(primary_tech_type_cleaned =gsub("[^[:alnum:]]", "", tolower(primary_tech_type))) 

hnmbr_2022 %>% 
  group_by(primary_energy_source) %>% 
  summarise(total_capacity_units = sum(capacity_heating_hot_water, na.rm = T), 
            total_generation_kwh = sum(generation_heating_hot_water, na.rm = T), 
            total_supply_kwh = sum(supply_heating_hot_water, na.rm = T)) 
```

## Match rate to previous data cycle 

Out of `r nrow(hnmbr_2022)` networks, we managed to match `r nrow(hnmbr_matched)` networks back to the previous (2018) data cycle. This equates to a `r (nrow(hnmbr_matched) / nrow(hnmbr_2022)) * 100`% match rate.  

### Comparison of network type

### Comparison of total Supply



